Assessing primitives performance\\ on multi-stage execution

### 2018-05-08 paper.tex
update

\subsection{Set-up}
Describe set-up:
GCC eval Ubuntu + machine spec
LLVM eval Mac OS X + machine spec.

>>>>

\subsection{Set-up}

Evaluaiton on x86 and not x64.

GCC eval Ubuntu + machine spec

The LLVM-Mac evaluaiton was performed on a MacBook pro with Mac OS 10.11.6, a 2.9Ghz processor Intel Core 5, 8 Gb 1867MHz DDR3 of RAM. The Mac VM was compiled using Apple LLVM version 8.0.0 (clang-800.0.38).
